Manuscript

### 2015-01-07 inst/simulation/manuscript.Rmd
...

```{r figure-3-init}
populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames)
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

@@

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- scenarioNames
  return(credibilityIntervals)  
}

@@

>>>>

```{r figure-3-init-2}
registerDoMC(cores=10) # The nodes seem to run out of memory and fail with a bogus error message, so it's better to reduce the number of used cores.

populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames)
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

registerDoMC(cores=detectCores())

@@

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=2)
  return(credibilityIntervals)  
}

@@

  p <- ggplot(cip2, aes(scenario, Proportion, shape=Interval, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)
